---
title: "Homework 5"
output: github_document
---

```{r, include = FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(rvest)
library(patchwork)
library(tidyverse)
library(p8105.datasets)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```
### Problem 1

The code chunk below imports the data in individual spreadsheets contained in `./data/zip_data/`. To do this, I create a dataframe that includes the list of all files in that directory and the complete path to each file. As a next step, I `map` over paths and import data using the `read_csv` function. Finally, I `unnest` the result of `map`.

```{r}
full_df = 
  tibble(
    files = list.files("data/zip_data/"),
    path = str_c("data/zip_data/", files)
  ) %>% 
  mutate(data = map(path, read_csv)) %>% 
  unnest()
```

The result of the previous code chunk isn't tidy -- data are wide rather than long, and some important variables are included as parts of others. The code chunk below tides the data using string manipulations on the file, converting from wide to long, and selecting relevant variables. 

```{r}
tidy_df = 
  full_df %>% 
  mutate(
    files = str_replace(files, ".csv", ""),
    group = str_sub(files, 1, 3)) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "outcome",
    names_prefix = "week_") %>% 
  mutate(week = as.numeric(week)) %>% 
  select(group, subj = files, week, outcome)
```

Finally, the code chunk below creates a plot showing individual data, faceted by group. 

```{r}
tidy_df %>% 
  ggplot(aes(x = week, y = outcome, group = subj, color = group)) + 
  geom_point() + 
  geom_path() + 
  facet_grid(~group)
```

This plot suggests high within-subject correlation -- subjects who start above average end up above average, and those that start below average end up below average. Subjects in the control group generally don't change over time, but those in the experiment group increase their outcome in a roughly linear way. 


### Problem 2

Describe the raw data. Create a city_state variable (e.g. “Baltimore, MD”) and then summarize within cities to obtain the total number of homicides and the number of unsolved homicides (those for which the disposition is “Closed without arrest” or “Open/No arrest”).

```{r}
homicide_df <- 
  read_csv("homicide-data.csv", na = c("", "Unknown")) %>% 
  mutate(city_state = str_c(city, ", ", state),
         resolution = case_when(
           disposition == "Closed without arrest" ~ "unsolved",
           disposition == "Open/No arrest" ~ "unsolved",
           disposition == "Closed by arrest" ~ "solved"
         )) %>% 
  relocate(uid, reported_date, city_state)
  
  homicide_df %>% 
    group_by(disposition,city) %>% 
  count() %>% 
    knitr::kable()
```
The raw data set has `r nrow(homicide_df)` rows and `r ncol(homicide_df)` columns and include variables such as  uid, reported date,  victim lastname, victim firstname,  victim race,  victim age,  victim sex,  city and  state.


Here we focus on Baltimore, MD to estimate the proportion of homicides that are unsolved as well as the confidence intervals.
```{r}
baltimore_summary <- 
 homicide_df %>% 
  filter(city_state == "Baltimore, MD") %>% 
  summarize(
    unsolved = sum(resolution == "unsolved"),
    n = n()
  )

baltimore_test <- 
  prop.test(
    x = baltimore_summary$unsolved,
    n = baltimore_summary$n) 

baltimore_test %>% 
  broom::tidy() %>% 
  select(estimate, starts_with("conf")) %>% 
  knitr::kable()
```
The estimated proportion is 0.6455 and the lower and upper confidence intervals are 0.628 and 0.663.


Next, we create a function for the proportions of unsolved homicides and the confidence intervals.
```{r}
prop_test_function = function(city_df) {
  city_summary =
    city_df %>%
    summarize(
      unsolved = sum(resolution == "unsolved"),
      n = n()
    )
  
  city_test =
    prop.test(
      x = city_summary %>% pull(unsolved),
      n = city_summary %>% pull(n))
  
  return(city_test)
}
```


```{r}
#iterate across all cities
results_df =
  homicide_df %>%
  nest(data = -city_state) %>%
  mutate(
    test_results = map(data, prop_test_function),
    tidy_results = map(test_results, broom::tidy)
  ) %>%
  select(city_state, tidy_results) %>%
  unnest(tidy_results) %>%
  select(city_state, estimate, starts_with("conf"))
results_df %>% knitr::kable()
```


I'll now create a plot that shows the estimates and confidence intervals for each city
```{r}
results_df %>%
  mutate(city_state = fct_reorder(city_state, estimate)) %>%
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme(axis.text.x = element_text(angle = 90, vjust = .5, hjust = 1)) +
  labs(title = "Proportion of Unsolved Homicides with Confidence Intervals", 
       x = "City and State",
       y = "Estimate of Unsolved Homicides")
```
From the plot above we see that Tulsa, AK has the lowest proportion of unsolved homicides but has the largest confidence intervals and Chicago, Il has the highest proportion of unsolved homicides with very small confidence intervals. Most of the other cities have reasonable confidence intervals.

### Problem 3

Generate 5000 datasets from the model with the following design elements:
Fix n=30
Fix σ=5
Set μ=0
```{r}
set.seed(0)

t_test_clean <- function(df) {
 out_df <- t.test(df,
         alternative = c("two.sided"),
         mu = 0,
         conf.level = 0.95) %>% 
    broom::tidy()
 return(out_df)
}


generate_results <- function(mu = 0, 
                             sigma=5,
                             n_iter=5000,
                             n_obs =30){

new_list <- list()


for (i in 1:n_iter) {
  temp_vec <- rnorm( n = n_obs, mean = mu, sd = sigma)
  new_list[[i]] <-temp_vec
}

stat_tib<-
  tibble(
  data = new_list
) %>% 
  mutate(
    t_test_res = map(.x = data, ~t_test_clean(.x))
  ) %>% 
  unnest(t_test_res) %>% 
 janitor::clean_names() %>% 
  select(estimate,p_value)

fin_tib <- stat_tib %>% 
  mutate(
    rej = p_value < 0.05
  ) %>% 
  summarise(
    total = n(),
    total_rej = sum(rej),
    prop_rej = total_rej/total,
    avg_mu_hat = mean(estimate)
    )
return(fin_tib)
}

mu_tib <-
  tibble(
    mu = c(0, 1, 2, 3, 4, 5, 6)
  ) %>% 
  mutate(
    results = map(.x = mu, ~generate_results(mu = .x))
  ) %>% 
  unnest(results)
```



Make a plot showing the proportion of times the null was rejected (the power of the test) on the y axis and the true value of μ
 on the x axis. Describe the association between effect size and power.
 
```{r}
mu_tib %>% 
  ggplot(aes(x = mu, y = prop_rej))+
  geom_point() + 
  xlab("True Mean") +
  ylab("Power")
```
 
Make a plot showing the average estimate of μ̂
 on the y axis and the true value of μ
 on the x axis. Make a second plot (or overlay on the first) the average estimate of μ̂
 only in samples for which the null was rejected on the y axis and the true value of μ
 on the x axis. 
```{r}
p <- mu_tib %>% 
  ggplot(aes(x = mu, y = avg_mu_hat))+
  geom_point() + 
  xlab("True Mean") +
  ylab("Average Mean")

q <- mu_tib %>% 
  ggplot(aes(x = mu, y = total_rej))+
  geom_point() +
  xlab("True Mean") +
  ylab("Total Rejected")
  
  p + q
```
 
 
 Is the sample average of μ̂
 across tests for which the null is rejected approximately equal to the true value of μ
? Why or why not?

Power is increaisng as true mean increases
